Probabilistic Forecast Reconciliation

### 2018-11-07 Presentation/ProbForeRec.tex
Few more edits on presentation

\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage[greek,english]{babel}

@@

\date{August 15, 2018}

@@

    \item Retail sales

@@

    	\item Aggregate of different product category sales
    	\item Further breakdown into individual stock keeping units.  

@@

  	\item Begin with a vector of forecasts that are incoherent.

@@

    	\only<2>{\item Let {\color{blue}$m$} be the bottom level series and {\color{blue}$\bm{b}$} be an {\color{blue}$m$}-vector of the bottom level series.}

@@

    The matrix ${\bm S}$ defines the aggregation constraints, e.g.

@@

	  The {\bf coherent subspace} is the linear subspace spanned by the columns of ${\bm S}$, i.e. $\mathfrak{s}=\mbox{sp}({\bm S})$

@@

  \item Projecting along this direction is more likely to result in a reconciled forecast closer to the target.

@@

      The probability measure $\nu$ is coherent if

@@

  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a linear function.  Then 

@@

  	Let the true predictive densities be elliptical.

@@

  		There exists a function $g(.)$ such that the true predictive distribution can be recovered by linear reconciliation as long as the unreconciled probabilistic forecast comes from the correct elliptical class.

@@

    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.  Conditions are also derived for when this $g(.)$ is also a projection.

@@

  		\item Then setting $\tilde{\bm y}^{[j]}=s\circ g(\hat{\bm y}^{[j]})=\bm{S}\bm{G}\hat{\bm y}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.

@@

  \begin{frame}{Univariate v Multivariate Scores}
    Scoring rules can be used to evaluate probabilistic forecasts

@@

    	\item Univariate
    		\item Continuous Rank Probability Score
    	\item Multivariate

@@

@@

    These may be computed using densities or a sample.
  \begin{frame}{Approaches}
  	\begin{enumerate}
  		\item Use a summary of all univariate scores.
  		\item Make comparisons on the joint distribution of bottom level series only.
        \item Make comparisons using the full joint distribution
  \end{enumerate}
  There are pitfalls to the third approach.

@@

	When comparing reconciled and unreconciled probabilistic forecasts on the basis of log score

@@

  \begin{frame}{Reconciled v Reconciled}
		\item For two reconciled probabilistic forecasts log score can be used.
		\item Comparisons can be made on the basis of bottom level series (or any basis series).
		\item By the definition of coherence $\log (f({\bm b}))=\log (f({\bm S}{\bm b}){\bm J})$
		\item The Jacobian does not affect the ordering of log score.
  \begin{frame}{Energy  score}
  		\item Using bottom level series only is a bad idea for energy score.
  		\item Energy score is invariant to orthogonal transformation but not affine transformations.
  		\item Since ${\bm S}$ is not a rotation the ranking of different methods based on the full hierarchy may differ from the ranking based on bottom level series only.

@@

>>>>

\documentclass[handout]{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage[greek,english]{babel}

@@

\date{November 14, 2018}

@@

    \item Wind power

@@

    	\item Forecasts required at a daily and hourly resolution.
    	\item Daily series is aggregate of 24 hourly series.  

@@

  	\item Begin with a vector of {\em base} forecasts that are incoherent.

@@

    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}$} be an {\color{blue}$m$}-vector of the bottom level series.}

@@

    The $n\times m$ matrix ${\bm S}$ defines the aggregation constraints, e.g.

@@

	  The {\bf coherent subspace} is the $m$-dimensional linear subspace of $\mathbb{R}^n$ spanned by the columns of ${\bm S}$, i.e. $\mathfrak{s}=\mbox{sp}({\bm S})$

@@

  \item Projecting along this direction is more likely to result in a reconciled forecast that is closer to the target.

@@

      The probability measure $\mu$ is coherent if

@@

  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a mapping.  Then 

@@

  	Consider case where the base true predictive distributions are elliptical.

@@

  		There exists a function $\bm{G}$ such that the true predictive distribution can be recovered by linear reconciliation.

@@

    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.  

@@

  		\item Then setting $\tilde{\bm y}^{[j]}=\bm{S}\bm{G}\hat{\bm y}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.

@@

  \begin{frame}{Multivariate Scores}

@@

    \item Scoring rules can be used to evaluate probabilistic forecasts

@@

	      \item Variogram score
    \item We may want to compare
    	\item Coherent v Incoherent
    	\item Coherent v Coherent

@@

@@

	When using log score

@@

@@

   		\item We have run lots of simulations
